Papers

### 2025-07-20 papers.qmd
Update website content and structure
Renamed sections in various files for clarity, changing 'Bin Yu' to 'Professor Bin Yu' in index.qmd and 'Select Publications' to 'Papers' in papers.qmd. Enhanced publication entries with direct links to papers for better accessibility. Updated the 'People' section title in people.qmd and changed 'Code' to 'Software' in software.qmd for consistency. Removed the outdated bio1.jpg image file.

# Select Publications

@@

A. R. Hsu, Y. Cherapanamjeri, A. Y. Odisho, P. R. Carroll, B. Yu (2024). [Mechanistic Interpretation through Contextual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886)

Y. S. Tan, O. Ronen, T. Saarinen, B. Yu (2024). [The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis.](https://arxiv.org/pdf/2406.19958)

O. Ronen, A. I. Humayun, R. Balestriero, R. Baraniuk, B. Yu (2024). [ScaLES: Scalable Latent Exploration Score for Pre-Trained Generative Networks](https://arxiv.org/pdf/2406.09657)

S. Hayou, N. Ghosh, B. Yu (2024). [The Impact of Initialization on LoRA Fineuning Dynamics.](https://arxiv.org/pdf/2406.08447)

B. Yu (2024). [After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1) (Harvard Data Science Review)

S. Hayou, N. Ghosh, B. Yu (2024). [LoRA+: Efficient Low Rank Adaptation of Large Models](https://arxiv.org/abs/2402.12354) (Proc. ICML)

C. F. Elliott, J. Duncan, T. M. Tang, M. Behr, K. Kumbier, B. Yu (2024). [Designing a data science simulation with MERITS: a primer.](https://arxiv.org/abs/2403.08971)

Y. Chen, C. Singh, X. Liu, S. Zuo, B. Yu, H. He, J. Gao (2024). [Towards consistent natural-language explanations via explanation-consistent finetuning.](https://arxiv.org/abs/2401.13986)

N. R. Mallinar, A. Zane, S. Frei, B. Yu (2024). Minimum-Norm Interpolation Under Covariate Shift. (Proc. ICML) [arXiv](https://arxiv.org/pdf/2404.00522)

L. Sun, A. Agarwal, A. Kornblith, B. Yu, C. Xiong (2024). ED-Copilot: Reduce Emergency Department Wait Time with Language Model Diagnostic Assistance. (Proc. ICML) [arXiv](https://arxiv.org/abs/2402.13448)

@@

C. Singh*, A. R. Hsu*, R. Antonello, S. Jain, A. G. Huth, B. Yu, J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)

Q. Zhang, C. Singh, L. Liu, X. Liu, B. Yu, J. Gao, T. Zhao (2023). [Tell your model where to attend: post-hoc attention steering for LLMs.](https://arxiv.org/abs/2311.02262)

Q. Wang*, T. M. Tang*, N. Youlton, C. S. Weldy, A. M. Kenney, O. Ronen, J. W. Hughes, E. T. Chin, S. C. Sutton, A. Agarwal, X. Li, M. Behr, K. Kumbier, C. S. Moravec, W. H. W. Tang, K. B. Margulies, T. P. Cappola, A. J. Buitte, R. Arnaout, J. B. Brown, J. R. Priest, V. N. Parikh, B. Yu*, E. Ashley* (2023). Epistasis regulates genetic control of cardiac hypertrophy. [medRxiv](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))

R. Cahill, Y. Wang, R. P. Xian, A. J. Lee, H. Zeng, B. Yu, B. Tasic, R. Abbasi-Asl (2023). Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology. [bioRxiv](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))

E. Irajizad, A. Kenney, T. Tang, J. Vykoukal, R. Wu, E. Murage, J. B. Dennison, M. Sans, J. P. Long, M. Loftus, J. A. Chabot, M. D. Kluger, F. Kastrinos, L. Brais, A. Babic, K. Jajoo, L. S. Lee, T. E. Clancy, K. Ng, A. Bullock, J. M. Genkinger, A. Maitra, K. A. Do, B. Yu, B. W. Wolpin, S. Hanash, J. F. Fahrmann. (2023). [A blood-based metabolomic signature predictive of risk for pancreatic cancer](https://pubmed.ncbi.nlm.nih.gov/37729870/). Cell Reports Medicine 4(9): 101194. doi: 10.1016/j.xcrm.2023.101194. (PCS related) ([Editorial](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10518497/))

R. Dwivedi, C. Singh, B. Yu, M. Wainwright (2023). [Revisiting miniumu description length complexity in overparametrized models.](https://jmlr.org/papers/v24/21-1133.html) JMLR, 24(268): 1-59.

K. Wu, Y. Chen, W. Ha, B. Yu (2023). [Prominent roles of conditionally invariant components in domain adaptation: theory and algorithms.](https://arxiv.org/abs/2309.10301) JMLR (accepted). [https://arxiv.org/abs/2309.10301](https://arxiv.org/abs/2309.10301)

N. Ghosh, S. Frei, W. Ha, B. Yu (2023). The effect of SGD batch size on autoencoder learning: sparsity, sharpness and feature learning. [https://arxiv.org/abs/2308.03215](https://arxiv.org/abs/2308.03215)

R. Netzorg, J. Li, B. Yu (2024). Improving prototypical part networks with reward reweighting, reselection, and retraining. Proc. ICML. [https://arxiv.org/abs/2307.03887](https://arxiv.org/abs/2307.03887)

A. Agarwal, A. M. Kenny, Y. S. Tan, T. M. Tang, B. Yu (2023). MDI+: a flexible random forest-based feature importance framework. [https://arxiv.org/abs/2307.01932](https://arxiv.org/abs/2307.01932) (PCS related)

A. R. Hsu, Y. Cherapanamjeri, B. Park, T. Naumann, A. Odisho, and B. Yu (2023). Diagnosing transformers: illuminating feature space for clinical decison-making. Proc. ICLR. [https://arxiv.org/abs/2305.17588](https://arxiv.org/abs/2305.17588)

C. Singh, A. R. Hsu, R. Antonello, S. Jain, A. G. Huth, B. Yu and J. Gao (2023). Explaining black box text modules in natural language with language models. [https://arxiv.org/abs/2305.09863](https://arxiv.org/abs/2305.09863)

@@

D. Shen, P. Ding, J. Sekhon, B. Yu (2022). Same root different leaves: time series and cross-sectional methods in panel data. Econometrica (accepted). [https://arxiv.org/abs/2207.14481](https://arxiv.org/abs/2207.14481)

B. Park, X. Wu, B. Yu, A. Zhou (2022). [Offline evaluation in RL: soft stability weighting to combine fitted Q-learning and model-based methods.](https://openreview.net/forum?id=R3h3-bt0mq) NeurIPS 3rd Offline Reinforcement Learning Workshop.

Y. S. Tan, C. Singh, K. Nasseri, A. Agarwal, J. Duncan, O. Ronen, M. Epland, A. Kornblith, B. Yu (2022). [Fast interpretable greedy-tree sums (FIGS)](https://arxiv.org/abs/2201.11931). ([imodels 🔎](https://github.com/csinva/imodels) contains code for FIGS)

A. Agarwal, Y. S. Tan, O. Ronen, C. Singh, B. Yu (2022). [Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods.](https://arxiv.org/abs/2202.00858) Proc. ICML ([imodels 🔎](https://github.com/csinva/imodels) contains code for hierarchical shrinkage (HS)).

B. Yu and C. Singh (2022). [Seven principles for rapid-response data science: lessons learned from covid-19 forecasting](https://projecteuclid.org/journals/statistical-science/volume-37/issue-2/Seven-Principles-for-Rapid-Response-Data-Science--Lessons-Learned/10.1214/22-STS855.full). Statistical Science, 36(2):266-269.

N. Ghosh, S. Mei, and B. Yu (2022). [The three stages of dynamics in high-dimensional kernel methods.](https://arxiv.org/abs/2111.07167) Proc. ICLR, 2022.

@@

Y. Tan, A. Agarwal, and B. Yu (2021). [A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds.](https://arxiv.org/abs/2110.09626) Proc. AISTATS.

N. Altieri, B. Park, J. DeNero, A. Odisho, B. Yu. (2021). [Improving natural language information extraction from cancer pathology reports using transfer learning and zero-shot string similarity.](https://pubmed.ncbi.nlm.nih.gov/34604711/) JAMIA Open. 2021 Sept. 30 4(3).

C. Singh, W. Ha and B. Yu (2021). [Interpreting and Improving Deep-Learning Models with Reality Checks](https://arxiv.org/abs/2108.06847). To appear in "xxAI - Beyond Explainable AI" (eds. Holzinger et al.).

W. Ha, C. Singh, F. Lanusse, S. Upadhyayula, and B. Yu (2021). [Adaptive Wavelet Distillation from Neural Networks through Interpretation.](https://nips.cc/Conferences/2021/ScheduleMultitrack?event=28027) Proc. NeurIPS 2021. ([code](https://github.com/Yu-Group/adaptive-wavelets))

M. Behr, Y. Wang, X. Li, B. Yu (2022). [Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests.](https://arxiv.org/abs/2102.11800) PNAS. ([theory for iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS-related)

N. Altieri, B. Park, M. Olson, J. DeNero, A. Odisho, B. Yu. (2021). Supervised line attention for tumor attribute classification from pathology reports: Higher performance with less data. Journal of Biomedical Informatics. 122 (2021) 103872. [arXiv version](https://arxiv.org/abs/2012.08113)

@@

M. Behr*, K. Kumbier*, A. Cordova-Palomera, M. Aguirre, E. Ashley, A. Butte, R. Arnaout, J. B. Brown, J. Preist*, B. Yu* (2020). [Learning epistatic polygenic phenotypes with Boolean interactions](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)

B. Norgeot*, G. Quer, B. K. Beaulieu-Jones, A. Torkamani, R. Dias, M. Gianfrancesco, R. Arnaout, I. S. Kohane, S. Saria, E. Topol, Z. Obermeyer, B. Yu & A. Butte* (2020). [Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist](https://www.nature.com/articles/s41591-020-1041-y), Nature Medicine, 26, 1320–1324.

B. Yu (2020). [Stability expanded, in reality](https://hdsr.mitpress.mit.edu/pub/ekrhsui8/release/1). Harvard Data Science Review (PCS related)

B. Yu and R. Barter (2020). [Data science process: one culture.](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1762615?journalCode=uasa20) JASA. (PCS related)

R. Dwivedi, Y. Tan, B. Park, M. Wei, K. Horgan, D. Madigan, B. Yu (2020). [Stable discovery of interpretable subgroups via calibration in causal studies (staDISC).](https://onlinelibrary.wiley.com/doi/10.1111/insr.12427) International Statistical Review ([code](https://github.com/Yu-Group/stadisc)) (PCS case study for causal inference)

X. Li, T. M. Tang, X. Wang, J. A. Kocher, B. Yu (2020). [A stability-driven protocol for drug response interpretable prediction (staDRIP)](https://arxiv.org/abs/2011.06593). NeurISP workshop on ML4H (Machine learning for Health) Extended Abstract.

A. Y. Odisho, B. Park, N. Altieri, J. DeNero, M. R Cooperberg, P. R .Carroll, B. Yu (2020). [Natural language processing systems for pathology parsing in limited data environments with uncertainty estimation.](https://academic.oup.com/jamiaopen/article/3/3/431/5922788) JAMIA Open.

L. Reiger, J. W. Murdoch, S. Singh, B. Yu (2020). [Interpretations are Useful: Penalizing Explanations to Align Neural Networks with Prior Knowledge](https://proceedings.icml.cc/static/paper_files/icml/2020/992-Paper.pdf). ICML Proceedings. ([code](https://github.com/laura-rieger/deep-explanation-penalization))

C. Singh, W. Ha, F. Lanusse, V. Boehm, J. Liu, B. Yu (2020). [Transformation Importance with Applications to Cosmology](https://arxiv.org/pdf/2003.01926.pdf) ICLR Workshop paper. ([code](https://github.com/csinva/transformation-importance))

N. Altieri, R. Barter, J. Duncan, R. Dwivedi, K. Kumbier, X. Li, R. Netzorg, B. Park, C. Singh*, Y. Tan, T.Tang, Y. Wang, C. Zhang, B. Yu*. (2020) [Curating a COVID-19 data repository and forecasting county-level death counts in the United States.](https://hdsr.mitpress.mit.edu/pub/p6isyf0g/release/1) Harvard Data Science Review ([code](https://github.com/Yu-Group/covid19-severity-prediction)) [7-day prediction results](https://covidseverity.com/) [Short talk video](https://www.stat.berkeley.edu/~binyu/ps/papers2020/RDSS20-yu.mp4)

B. Yu and K. Kumbier (2020) [Veridical data science](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-YuKumbier.pdf) (PCS framework), PNAS. 117 (8), 3920-3929. [QnAs with Bin Yu.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-QnAsBinYu.pdf)

R. Dwivedi, N. Ho, K. Khamaru, M. J. Wainwright, M. I. Jordan and B. Yu (2020) [Sharp Analysis of Expectation-Maximization for Weakly Identifiable Mixture Models](https://arxiv.org/abs/1902.00194) AISTATS.

R. Dwivedi, N. Ho, K. Khamaru, M. J. Wainwright, M. I. Jordan and B. Yu (2020) [Singularity, Misspecification and the Convergence Rate of EM](https://arxiv.org/abs/1810.00828) Annals of Statistics.

Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2020) [Fast Mixing of Metropolized Hamiltonian Monte Carlo: Benefits of Multi-Step Gradients,](https://www.jmlr.org/papers/volume21/19-441/19-441.pdf) JMLR, [arXiv](https://arxiv.org/abs/1905.12247)

@@

R. Dwivedi, Y. Chen, M. J. Wainwright and B. Yu (2019) [Log-concave Sampling: Metropolis Hastings Algorithms are Fast](http://jmlr.org/papers/v20/19-306.html) JMLR.

D. Rothenhäusler and B. Yu (2019). [Incremental causal effects](https://arxiv.org/abs/1907.13258).

@@

Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2018) [Fast MCMC Algorithms on Polytopes](http://jmlr.org/papers/v19/18-158.html). JMLR . http://jmlr.org/papers/v19/18-158.html

Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2020) [Vaidya Walk: A Sampling Algorithm Based on Volumetric-Logarithmic Barrier](https://ieeexplore.ieee.org/abstract/document/8262876/) Allerton Conference 2017 https://ieeexplore.ieee.org/abstract/document/8262876/

W. J. Murdoch, C. Singh, K. Kumbier, R. Abbasi-Asl, and B. Yu* (2019) [Definitions, methods, and applications in interpretable machine learning.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/iML19-Murdochetal.pdf) PNAS, 116 (44) 22071-22080.

W. J. Murdoch, C. Sign, and B. Yu (2019). [Hierarchical interpretations for neural network predictions.](https://openreview.net/pdf?id=SkEqro0ctQ) ICLR. ([code](https://github.com/csinva/hierarchical-dnn-interpretations))

Y. Wang, S. Wu and B. Yu (2020) [Unique Sharp Local Minimum in l1-minimization Complete Dictionary Learning.](https://jmlr.org/papers/volume21/19-169/19-169.pdf) JMLR. 21(63), pp. 1-52. Also at https://arxiv.org/abs/1902.08380

Y. Chen, R. Abbasi-Asl, A. Bloniarz, M. Oliver, B. Willmore, J. Gallant*, and B. Yu* (2018) [The DeepTune framework for modeling and characterizing neurons in visual cortex area V4](https://www.biorxiv.org/content/10.1101/465534v1) https://www.biorxiv.org/content/10.1101/465534v1

K. Kumbier, S. Sumanta, J. B. Brown, S. Celniker, and B. Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) [https://arxiv.org/abs/1810.0728](https://arxiv.org/abs/1810.0728) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)

Y. Chen C. Jin, and B. Yu (2018) [Stability and Convergence Trade-off of Iterative Optimization Algorithms.](https://arxiv.org/abs/1804.01619) https://arxiv.org/abs/1804.01619

J. Murdoch, P. Liu, and B. Yu (2018) [Beyond word importance: contextual decomposition to extract interactions from LSTMs.](https://arxiv.org/abs/1801.05453) Proc. ICLR 2018. [https://arxiv.org/abs/1705.07356](https://arxiv.org/abs/1705.07356) ([code)](https://github.com/csinva/hierarchical-dnn-interpretations)

R. Diwivedi, Y. Chen, M. J. Wainwright, and B. Yu (2018) [Log-concave sampling: Metropolis-Hastings algorithms are fast!](https://arxiv.org/abs/1801.02309) https://arxiv.org/abs/1801.02309.

>>>>

# Papers

@@

A. R. Hsu, Y. Cherapanamjeri, A. Y. Odisho, P. R. Carroll, B. Yu (2024). Mechanistic Interpretation through Contextual Decomposition in Transformers. ([paper](https://arxiv.org/pdf/2407.00886))

Y. S. Tan, O. Ronen, T. Saarinen, B. Yu (2024). The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis. ([paper](https://arxiv.org/pdf/2406.19958))

O. Ronen, A. I. Humayun, R. Balestriero, R. Baraniuk, B. Yu (2024). ScaLES: Scalable Latent Exploration Score for Pre-Trained Generative Networks. ([paper](https://arxiv.org/pdf/2406.09657))

S. Hayou, N. Ghosh, B. Yu (2024). The Impact of Initialization on LoRA Fineuning Dynamics. ([paper](https://arxiv.org/pdf/2406.08447))

B. Yu (2024). After Computational Reproducibility: Scientific Reproducibility and Trustworthy AI. (Harvard Data Science Review) ([paper](https://hdsr.mitpress.mit.edu/pub/8qexde24/release/1))

S. Hayou, N. Ghosh, B. Yu (2024). LoRA+: Efficient Low Rank Adaptation of Large Models. (Proc. ICML) ([paper](https://arxiv.org/abs/2402.12354))

C. F. Elliott, J. Duncan, T. M. Tang, M. Behr, K. Kumbier, B. Yu (2024). Designing a data science simulation with MERITS: a primer. ([paper](https://arxiv.org/abs/2403.08971))

Y. Chen, C. Singh, X. Liu, S. Zuo, B. Yu, H. He, J. Gao (2024). Towards consistent natural-language explanations via explanation-consistent finetuning. ([paper](https://arxiv.org/abs/2401.13986))

N. R. Mallinar, A. Zane, S. Frei, B. Yu (2024). Minimum-Norm Interpolation Under Covariate Shift. (Proc. ICML) ([paper](https://arxiv.org/pdf/2404.00522))

L. Sun, A. Agarwal, A. Kornblith, B. Yu, C. Xiong (2024). ED-Copilot: Reduce Emergency Department Wait Time with Language Model Diagnostic Assistance. (Proc. ICML) ([paper](https://arxiv.org/abs/2402.13448))

@@

C. Singh*, A. R. Hsu*, R. Antonello, S. Jain, A. G. Huth, B. Yu, J. Gao (2023). Explaining black box text modules in natural language with language models. ([paper](https://arxiv.org/abs/2305.09863))

Q. Zhang, C. Singh, L. Liu, X. Liu, B. Yu, J. Gao, T. Zhao (2023). Tell your model where to attend: post-hoc attention steering for LLMs. ([paper](https://arxiv.org/abs/2311.02262))

Q. Wang*, T. M. Tang*, N. Youlton, C. S. Weldy, A. M. Kenney, O. Ronen, J. W. Hughes, E. T. Chin, S. C. Sutton, A. Agarwal, X. Li, M. Behr, K. Kumbier, C. S. Moravec, W. H. W. Tang, K. B. Margulies, T. P. Cappola, A. J. Buitte, R. Arnaout, J. B. Brown, J. R. Priest, V. N. Parikh, B. Yu*, E. Ashley* (2023). Epistasis regulates genetic control of cardiac hypertrophy. ([paper](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1)) ([code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))

R. Cahill, Y. Wang, R. P. Xian, A. J. Lee, H. Zeng, B. Yu, B. Tasic, R. Abbasi-Asl (2023). Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology. ([paper](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2)) ([code](https://github.com/abbasilab/osNMF))

E. Irajizad, A. Kenney, T. Tang, J. Vykoukal, R. Wu, E. Murage, J. B. Dennison, M. Sans, J. P. Long, M. Loftus, J. A. Chabot, M. D. Kluger, F. Kastrinos, L. Brais, A. Babic, K. Jajoo, L. S. Lee, T. E. Clancy, K. Ng, A. Bullock, J. M. Genkinger, A. Maitra, K. A. Do, B. Yu, B. W. Wolpin, S. Hanash, J. F. Fahrmann. (2023). A blood-based metabolomic signature predictive of risk for pancreatic cancer. Cell Reports Medicine 4(9): 101194. doi: 10.1016/j.xcrm.2023.101194. (PCS related) ([paper](https://pubmed.ncbi.nlm.nih.gov/37729870/)) ([Editorial](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10518497/))

R. Dwivedi, C. Singh, B. Yu, M. Wainwright (2023). Revisiting miniumu description length complexity in overparametrized models. JMLR, 24(268): 1-59. ([paper](https://jmlr.org/papers/v24/21-1133.html))

K. Wu, Y. Chen, W. Ha, B. Yu (2023). Prominent roles of conditionally invariant components in domain adaptation: theory and algorithms. JMLR (accepted). ([paper](https://arxiv.org/abs/2309.10301))

N. Ghosh, S. Frei, W. Ha, B. Yu (2023). The effect of SGD batch size on autoencoder learning: sparsity, sharpness and feature learning. ([paper](https://arxiv.org/abs/2308.03215))

R. Netzorg, J. Li, B. Yu (2024). Improving prototypical part networks with reward reweighting, reselection, and retraining. Proc. ICML. ([paper](https://arxiv.org/abs/2307.03887))

A. Agarwal, A. M. Kenny, Y. S. Tan, T. M. Tang, B. Yu (2023). MDI+: a flexible random forest-based feature importance framework. (PCS related) ([paper](https://arxiv.org/abs/2307.01932))

A. R. Hsu, Y. Cherapanamjeri, B. Park, T. Naumann, A. Odisho, and B. Yu (2023). Diagnosing transformers: illuminating feature space for clinical decison-making. Proc. ICLR. ([paper](https://arxiv.org/abs/2305.17588))

C. Singh, A. R. Hsu, R. Antonello, S. Jain, A. G. Huth, B. Yu and J. Gao (2023). Explaining black box text modules in natural language with language models. ([paper](https://arxiv.org/abs/2305.09863))

@@

D. Shen, P. Ding, J. Sekhon, B. Yu (2022). Same root different leaves: time series and cross-sectional methods in panel data. Econometrica (accepted). ([paper](https://arxiv.org/abs/2207.14481))

B. Park, X. Wu, B. Yu, A. Zhou (2022). Offline evaluation in RL: soft stability weighting to combine fitted Q-learning and model-based methods. NeurIPS 3rd Offline Reinforcement Learning Workshop. ([paper](https://openreview.net/forum?id=R3h3-bt0mq))

Y. S. Tan, C. Singh, K. Nasseri, A. Agarwal, J. Duncan, O. Ronen, M. Epland, A. Kornblith, B. Yu (2022). Fast interpretable greedy-tree sums (FIGS). ([paper](https://arxiv.org/abs/2201.11931)) ([code](https://github.com/csinva/imodels))

A. Agarwal, Y. S. Tan, O. Ronen, C. Singh, B. Yu (2022). Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods. Proc. ICML ([paper](https://arxiv.org/abs/2202.00858)) ([code](https://github.com/csinva/imodels)).

B. Yu and C. Singh (2022). Seven principles for rapid-response data science: lessons learned from covid-19 forecasting. Statistical Science, 36(2):266-269. ([paper](https://projecteuclid.org/journals/statistical-science/volume-37/issue-2/Seven-Principles-for-Rapid-Response-Data-Science--Lessons-Learned/10.1214/22-STS855.full))

N. Ghosh, S. Mei, and B. Yu (2022). The three stages of dynamics in high-dimensional kernel methods. Proc. ICLR, 2022. ([paper](https://arxiv.org/abs/2111.07167))

@@

Y. Tan, A. Agarwal, and B. Yu (2021). A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds. Proc. AISTATS. ([paper](https://arxiv.org/abs/2110.09626))

N. Altieri, B. Park, J. DeNero, A. Odisho, B. Yu. (2021). Improving natural language information extraction from cancer pathology reports using transfer learning and zero-shot string similarity. JAMIA Open. 2021 Sept. 30 4(3). ([paper](https://pubmed.ncbi.nlm.nih.gov/34604711/))

C. Singh, W. Ha and B. Yu (2021). Interpreting and Improving Deep-Learning Models with Reality Checks. To appear in "xxAI - Beyond Explainable AI" (eds. Holzinger et al.). ([paper](https://arxiv.org/abs/2108.06847))

W. Ha, C. Singh, F. Lanusse, S. Upadhyayula, and B. Yu (2021). Adaptive Wavelet Distillation from Neural Networks through Interpretation. Proc. NeurIPS 2021. ([paper](https://nips.cc/Conferences/2021/ScheduleMultitrack?event=28027)) ([code](https://github.com/Yu-Group/adaptive-wavelets))

M. Behr, Y. Wang, X. Li, B. Yu (2022). Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests. PNAS. (PCS-related) ([paper](https://arxiv.org/abs/2102.11800)) ([theory for iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115))

N. Altieri, B. Park, M. Olson, J. DeNero, A. Odisho, B. Yu. (2021). Supervised line attention for tumor attribute classification from pathology reports: Higher performance with less data. Journal of Biomedical Informatics. 122 (2021) 103872. ([paper](https://arxiv.org/abs/2012.08113))

@@

M. Behr*, K. Kumbier*, A. Cordova-Palomera, M. Aguirre, E. Ashley, A. Butte, R. Arnaout, J. B. Brown, J. Preist*, B. Yu* (2020). Learning epistatic polygenic phenotypes with Boolean interactions. (PCS inference case study) ([paper](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1)) ([code](https://github.com/merlebehr/epiTree))

B. Norgeot*, G. Quer, B. K. Beaulieu-Jones, A. Torkamani, R. Dias, M. Gianfrancesco, R. Arnaout, I. S. Kohane, S. Saria, E. Topol, Z. Obermeyer, B. Yu & A. Butte* (2020). Minimum information about clinical artificial intelligence modeling: the MI-CLAIM checklist, Nature Medicine, 26, 1320–1324. ([paper](https://www.nature.com/articles/s41591-020-1041-y))

B. Yu (2020). Stability expanded, in reality. Harvard Data Science Review (PCS related) ([paper](https://hdsr.mitpress.mit.edu/pub/ekrhsui8/release/1))

B. Yu and R. Barter (2020). Data science process: one culture. JASA. (PCS related) ([paper](https://www.tandfonline.com/doi/abs/10.1080/01621459.2020.1762615?journalCode=uasa20))

R. Dwivedi, Y. Tan, B. Park, M. Wei, K. Horgan, D. Madigan, B. Yu (2020). Stable discovery of interpretable subgroups via calibration in causal studies (staDISC). International Statistical Review (PCS case study for causal inference) ([paper](https://onlinelibrary.wiley.com/doi/10.1111/insr.12427)) ([code](https://github.com/Yu-Group/stadisc))

X. Li, T. M. Tang, X. Wang, J. A. Kocher, B. Yu (2020). A stability-driven protocol for drug response interpretable prediction (staDRIP). NeurISP workshop on ML4H (Machine learning for Health) Extended Abstract. ([paper](https://arxiv.org/abs/2011.06593))

A. Y. Odisho, B. Park, N. Altieri, J. DeNero, M. R Cooperberg, P. R .Carroll, B. Yu (2020). Natural language processing systems for pathology parsing in limited data environments with uncertainty estimation. JAMIA Open. ([paper](https://academic.oup.com/jamiaopen/article/3/3/431/5922788))

L. Reiger, J. W. Murdoch, S. Singh, B. Yu (2020). Interpretations are Useful: Penalizing Explanations to Align Neural Networks with Prior Knowledge. ICML Proceedings. ([paper](https://proceedings.icml.cc/static/paper_files/icml/2020/992-Paper.pdf)) ([code](https://github.com/laura-rieger/deep-explanation-penalization))

C. Singh, W. Ha, F. Lanusse, V. Boehm, J. Liu, B. Yu (2020). Transformation Importance with Applications to Cosmology. ICLR Workshop paper. ([paper](https://arxiv.org/pdf/2003.01926.pdf)) ([code](https://github.com/csinva/transformation-importance))

N. Altieri, R. Barter, J. Duncan, R. Dwivedi, K. Kumbier, X. Li, R. Netzorg, B. Park, C. Singh*, Y. Tan, T.Tang, Y. Wang, C. Zhang, B. Yu*. (2020) Curating a COVID-19 data repository and forecasting county-level death counts in the United States. Harvard Data Science Review ([paper](https://hdsr.mitpress.mit.edu/pub/p6isyf0g/release/1)) ([code](https://github.com/Yu-Group/covid19-severity-prediction)) ([7-day prediction results](https://covidseverity.com/)) ([Short talk video](https://www.stat.berkeley.edu/~binyu/ps/papers2020/RDSS20-yu.mp4))

B. Yu and K. Kumbier (2020) Veridical data science (PCS framework), PNAS. 117 (8), 3920-3929. ([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-YuKumbier.pdf)) ([QnAs with Bin Yu](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-QnAsBinYu.pdf))

R. Dwivedi, N. Ho, K. Khamaru, M. J. Wainwright, M. I. Jordan and B. Yu (2020) Sharp Analysis of Expectation-Maximization for Weakly Identifiable Mixture Models AISTATS. ([paper](https://arxiv.org/abs/1902.00194))

R. Dwivedi, N. Ho, K. Khamaru, M. J. Wainwright, M. I. Jordan and B. Yu (2020) Singularity, Misspecification and the Convergence Rate of EM Annals of Statistics. ([paper](https://arxiv.org/abs/1810.00828))

Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2020) Fast Mixing of Metropolized Hamiltonian Monte Carlo: Benefits of Multi-Step Gradients. JMLR, ([paper](https://www.jmlr.org/papers/volume21/19-441/19-441.pdf)) ([arXiv](https://arxiv.org/abs/1905.12247))

@@

R. Dwivedi, Y. Chen, M. J. Wainwright and B. Yu (2019) Log-concave Sampling: Metropolis Hastings Algorithms are Fast JMLR. ([paper](http://jmlr.org/papers/v20/19-306.html))

D. Rothenhäusler and B. Yu (2019). Incremental causal effects. ([paper](https://arxiv.org/abs/1907.13258))

@@

Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2018) [Fast MCMC Algorithms on Polytopes.](http://jmlr.org/papers/v19/18-158.html) JMLR.

Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2020) Vaidya Walk: A Sampling Algorithm Based on Volumetric-Logarithmic Barrier. Allerton Conference 2017. ([paper](https://ieeexplore.ieee.org/abstract/document/8262876/))

W. J. Murdoch, C. Singh, K. Kumbier, R. Abbasi-Asl, and B. Yu* (2019) Definitions, methods, and applications in interpretable machine learning. PNAS, 116 (44) 22071-22080. ([paper](https://www.stat.berkeley.edu/~binyu/ps/papers2020/iML19-Murdochetal.pdf))

W. J. Murdoch, C. Sign, and B. Yu (2019). Hierarchical interpretations for neural network predictions. ICLR. ([paper](https://openreview.net/pdf?id=SkEqro0ctQ)) ([code](https://github.com/csinva/hierarchical-dnn-interpretations))

Y. Wang, S. Wu and B. Yu (2020) Unique Sharp Local Minimum in l1-minimization Complete Dictionary Learning. JMLR. 21(63), pp. 1-52. ([paper](https://jmlr.org/papers/volume21/19-169/19-169.pdf)) ([arXiv](https://arxiv.org/abs/1902.08380))

Y. Chen, R. Abbasi-Asl, A. Bloniarz, M. Oliver, B. Willmore, J. Gallant*, and B. Yu* (2018) The DeepTune framework for modeling and characterizing neurons in visual cortex area V4. ([paper](https://www.biorxiv.org/content/10.1101/465534v1))

K. Kumbier, S. Sumanta, J. B. Brown, S. Celniker, and B. Yu* (2018) Refining interaction search through signed iterative Random Forests. (an enhanced version of iRF, PCS related) ([paper](https://arxiv.org/abs/1810.07287)) ([iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115))

Y. Chen C. Jin, and B. Yu (2018) Stability and Convergence Trade-off of Iterative Optimization Algorithms. ([paper](https://arxiv.org/abs/1804.01619))

J. Murdoch, P. Liu, and B. Yu (2018) Beyond word importance: contextual decomposition to extract interactions from LSTMs. Proc. ICLR 2018. ([paper](https://arxiv.org/abs/1801.05453)) ([code](https://github.com/csinva/hierarchical-dnn-interpretations))

R. Diwivedi, Y. Chen, M. J. Wainwright, and B. Yu (2018) Log-concave sampling: Metropolis-Hastings algorithms are fast! ([paper](https://arxiv.org/abs/1801.02309))
